### 2017-02-27 2017mergingmerges/section/03-Definition.tex
Rename XX-Fusion.tex to 04-Fusion.tex

As we cannot encode all possible evaluation orderings into the definition of the processes themselves, we have defined the evaluation rules to admit many possible orderings. In a direct implementation of concurrent processes using message passing and operating system threads, an actual, working, evaluation order would be discovered dynamically at runtime. In contrast, the role of our fusion transform is to determine one of these working evaluation orders statically. In the fused result process, the instructions will be scheduled so that they run in one of the orders that we would have gotten if the process group was executed dynamically. In doing so, we also eliminate the need to pass messages between processes --- once they are fused we can just copy values between heap locations.

>>>>

As we cannot encode all possible evaluation orderings into the definition of the processes themselves, we have defined the evaluation rules to admit many possible orderings. In a direct implementation of concurrent processes using message passing and operating system threads, an actual, working, evaluation order would be discovered dynamically at runtime. In contrast, the role of our fusion transform is to construct one of these working evaluation orders statically. In the fused result process, the instructions will be scheduled so that they run in one of the orders that would have arisen if the process group was executed dynamically. In doing so, we also eliminate the need to pass messages between processes --- once they are fused we can just copy values between heap locations.
